Explain urban regional function

### 2018-10-30 paper.tex
Add files via upload
Introduction和Related work

\documentclass[runningheads]{llncs}
\usepackage{graphicx}

@@

\keywords{Explanation  \and Urban computing \and Sentiment analysis.}
\end{abstract}
%

@@

\subsection{motivation}
Urban computing~\cite{Zheng2014UrbanConcepts} is defined as a concept where many factors ,such as sensors,prople,vehicles and so on, consist of a dynamic urban system. %?
The aims of urban computing include improving the living quality of residents, optimizing urban planning, decreasing traffic jams, reducing various pollution and so on.
With the improvement of living life of urban residents, GPS-embedded taxi begin to play an important part of urban computing. 
And the data of taxi mobility provide us an valuable way to compute urban system.For example,Zheng et al. ~\cite{Zheng2011taxicabs} detect the flaws in the existing urban planning of a city using the GPS trajectories of taxis traveling in the urban areas. Meng et al.\cite{Meng2017Traffic} propose a framework to infer the city-wide traffic volume information with loop detectors and taxi trajectories. Garg et al.\cite{Garg2018Route}minimizing distance through Monte Carlo tree search to decrease the rate of empty carrying and improve taxi drivers’ profits.
As you can see, Urban computing is closely linked with urban life.

Discovering regions of different function is a step towards urban computing.In this direction, Yuan et al.~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion,Yuan2018FunctionRegion} do well in discovering regions of different functions %3 references.
%~\cite{Yuan2012FunctionRegion}~\cite{Yuan2015FunctionRegion}:latent activity trajectories~\cite{Yuan2018FunctionRegion}
% reference
without explanation

%+figure

syst
%Explaining the result is of crucial importance
We can see that early recommendation systems tend to base on intuition and full with common sense,which improve users' satisfaction easily. Now the explanation recommendation systems is developing with more accuracy , which generate more satisfying results.Nevertheless ,the complexity of models is increasing at the meantime,which covers the intuition of whole structure and weakens the persuasiveness of models.So the explanation is playing an important part in recommendation systems.%~\cite{{Zhang2018SIGIR}}
Majority of users trust and choice satisfaction were highly correlated with the reliability of the explanations for recommendations.Herlocker et al.~\cite{Herlocker2000Explanation}  do an investigation which shows that explanation facilities can improve the acceptance of recommendation systems.The following experiments,e.g.,by Ferwerda et al.~\cite{Ferwerda2012ContentCorrelate} has proven the conclusion.We aim to propose models to explain the destination why we recommend it more persuasively

%explain implementation, we need to incorporate activity and online sentiment
Our goal is to proposed a model to predict taxi destination and provide persuasive explanation for it.
input: mobility data
output: identify urban region, label temporal function of region, explain function aspect-opinion-sentiment
%Furthermore, provide xxx explaination, activity , focus on aspects

\begin{figure}
    \centering
    \includegraphics[scale=0.25]{Structure.png}
    \caption{The general structure of our paper}
    %\label{fig:my_label}
\end{figure}

\subsection{problem}
For solve the problem,we face two challenges.One of it is...and the other is ...
segment regions = group regions with similar functions

function = distribution of activitys and opinions

%challenge

previous research
aspect urban related

@@

%second challenge: time bins
urban region : function temporal 
mobility data temporal information not fully utilized

\subsection{contribution}
Our paper has an outstanding result in following several aspect:
\begin{itemize}
  \item According to what I have learned,we are the first one to state-of-the-art
  \item 2
  \item 3
\end{itemize}

@@

Two lines of work are related to this paper: sentiment analysis into human mobility,content from social media also provide great help for us. Many scholars have made fundamental contributions,and we combined them to find interesting patterns and extended the application .

To the best of our knowledges,we are the first to combined the sentiment into human mobility.

@@

Urban computing~\cite{Zheng2014UrbanConcepts} tackles the major issues that cities face by analyzing human mobility collected from different sensors.  
Major sources of human mobility data are checkins in POI~\cite{}, pick-up and drop-off behavior of taxicabs~\cite{} in different locations and  trajectories~\cite{}.
%extract the different among these data
For checkins data, the most commonly adopted model is.
For taxicabs data, to fully utilize pick-up and drop-off, xxx is adopted to enhance xxx
For trajectory data, as it involves multiple points

%tasks
The aim of mobility mining is to uncover informative patterns of improve incomes of taxi drivers~\cite{}, attracts an increasing research interest~\cite{}. 
However, existing urban computing systems extensively rely on complex machine learning algorithms hence they act as blank-boxes for end users. 
The lack of explainability weakens the persuasiveness and trustworthiness of the system for users
Our work is to provide intuitive explanations of the results for users or system designers
%most of them adopt a topic model, treating mobility patterns as words~\cite{}%topic models

@@

Recently, an emrging research interest is witnessed in exploring the geographical factors that affect online sentiment.
Empirical studies have been conducted on large-scale human mobility data, such as checkins~\cite{}, trajectory, xxx~\cite{}
Associations are found between online sentiments and geographical factors, e.g happy regions are more likely to connect with each other~\cite{milan15},a high check-in density region usually presents a more positive moode~\cite{},

%complete survey
However, most existing work of this line employ simple statistical analysis to uncover the associations. 
Such a coarse-grained analysis is distorted by latent variables, such as activity of the region.
Our work is the first to incorporate activity to obtain a fine-grained analysis.

@@

\section{Experiments}

\subsection{Data Set}
The data set for our experiments including both mobility data and content data.
The mobility data including the pick-up and drop-off time and coordinates in November of the year 2016 provided by DiDi, the biggest taxi platform in China.It contributed to the movement pattern of human mobility.
And the online content is crawled from a website with many comments similar to Yelp called DazhongDianping and a social media named Weibo , which helps sentiment analysis of the regions.

@@

\begin{thebibliography}{25}
\bibitem{Zheng2014UrbanConcepts}Zheng Y, Capra L, Wolfson O, et al. Urban Computing:Concepts, Methodologies, and Applications[J]. Acm Transactions on Intelligent Systems \& Technology, 2014, 5(3):1-55.
    %综述城市计算的概念和框架
\bibitem{Zheng2011taxicabs}Zheng Y, Liu Y, Yuan J, et al. Urban computing with taxicabs[C]// International Conference on Ubiquitous Computing. ACM, 2011:89-98.
    %利用GPS轨迹检测出现有城市规划中存在的缺陷。结果包括：1）存在显著交通问题的区域对，2）连接结构以及它们之间的相关性。这些结果可以评估所实施的规划的有效性，例如一个城市新建的公路和地铁线路，并提醒城市规划者在构思未来规划时没有认识到的问题。
\bibitem{Meng2017Traffic} Meng, C.; Yi, X.; Su, L.; Gao, J.; Zheng, Y. City-wide Traffic Volume Inference with Loop Detector Data and Taxi Trajectories. Proceedings of the 25th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems,ACM,2017, 1:1-1:10 
    %提出了一个框架来推断城市交通流量信息与环路探测器和出租车轨迹。

@@

@@

@@

@@

\bibitem{Resnick1994UserBased}Resnick P, Iacovou N, Suchak M, et al. GroupLens:an open architecture for collaborative filtering of netnews[C]// ACM Conference on Computer Supported Cooperative Work. ACM, 1994:175-186.
    %提出user-based collaboration filtering
\bibitem{Sarwar2001ItemBased}Sarwar B, Karypis G, Konstan J, et al. Item-based collaborative filtering recommendation algorithms[C]// International Conference on World Wide Web. ACM, 2001:285-295.
    %提出item-based collaboration filtering
\bibitem{Pazzani2007ContentBased}Pazzani M J, Billsus D. Content-based recommendation systems[M]// The adaptive web. Springer-Verlag, 2007:325-341.
    %提出content-based collaboration filtering    

@@

@@

\bibitem{}
\bibitem{}
\bibitem{}
\bibitem{}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{subfigure}

@@

\keywords{Explanation  \and Urban computing \and Online content \and Sentiment analysis.}
\end{abstract}
%

@@

\subsection{motivation}
%urban computing
Urban computing, defined in~\cite{Zheng2014UrbanConcepts} as a process of acquisition, integration and analysis of big and heterogeneous data generated by diverse sources in urban spaces.%definition
One of the most important data source is human mobility data, e.g. pick-ups and drop-offs of taxicabs.
Such mobility data can contribute to improve living quality of residents, e.g. optimizing urban planning~\cite{Zheng2011taxicabs}, easing traffic congestion~\cite{Meng2017Traffic}, decreasing energy consumption ~\cite{Zhang2015Fuel}, reducing air pollution~\cite{Shang2014Pollution} and so on.
Therefore, mining and modeling mobility data has attracted attentions from both academia and industry.

%region function
Identifying functional regions has been a critical step towards efficient government administration and policy making for decades.
In early work, a functional region was defined as a geographical region where the majority of local population recruit and are employed within the region \cite{Ball1980Definition}.
Due to the availability of large-scale mobility data, an increasing amount of data-driven approaches~\cite{Farmer2009Overview} have been proposed.
Most of them use clustering methods on commuting data, such as origin-destination pairs of labour market data ~\cite{Karlsson2006FunctionalRegionSummary} while others use remote-sensor image data~\cite{Vatsavai2011Remote}.
Later work focuses on city-level functional region identification, where a functional region is a region in a city which supports different needs of people’s urban lives~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
To obtain accurate identification, recent research tends to use complex models for various form of data,
e.g. DRoF based on Dirichlet Multinomial
Regression with latent factors applying in mobility data of taxicabs and points of interests (POIs)~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}, clustering algorithms based on the 'modularity function'~\cite{Newman2004ModularityFunction} applying in telecommunication~\cite{Ratti2010Telecom},unsupervised semantic labeling framework based on the Latent Dirichlet Allocation applying in remote-sensor data~\cite{Vatsavai2010Remote}. %complex model

%explainability
Explanation is regarded as a reason or justification given for an action or a plan.
Majority of trustiness and satisfaction were highly correlated with the reliability of the explanations~\cite{Herlocker2000Explanation}.
The complex nature of these models covers the intuition explanation of the system,which weakens the interpretability to end users and system designers.%The lack of explanation of the identification xxx
To fit with the growth of complex models,there is an emerging trend in studying explainable AI~\cite{Preece2018ExplainAI}.
For example,graph and text with templates explanation is provided in navigation~\cite{Korpan2017navigation} and cognitive cities~\cite{Jose2018cognitive} to improve trustiness of people.%explainable AI reference, data mining
%Interpretable fuzzy systems have already successfully contributed to build explainable AI systems for cognitive cities.
%the report combines both NL texts and graphs with the aim of maximizing interpretability.
To the best of our knowledge, none of the previous urban functional identification provide explanation for the results of region segmentation and functional labels automatically.
To make the result more convinced,we aim to propose models to explain the identification of urban functional explanation.

%explain implementation, we need to incorporate activity and online sentiment
In this paper,our goal is to proposed a model to explanation for our functional region clustering results.
We have two data sets. One is mobility data 3 million including pick-up and drop-off coordinates and time,which provide detailed moving pattern for the dynamic urban system to discovering regions with different functions.
And the other is comment data with shop address that reveal sentiment tendencies of the shop.We could exact labels as the form of 'character-opinion-sentiment' from and pick labels with strongest sentiment as our explanation.
We combined the urban computing using mobility data with sentiment analysis using geo-content.
Fig.\ref{explanation-example} reveal an example of our output of model.
%Furthermore, provide xxx explanation, activity , focus on aspects

%input
%output
\begin{figure}
\centering
\subfigure[An example of our identification result]{
\label{real-map} %% label for first subfigure
\includegraphics[width=2in]{example-net.png}}
\hspace{0.1in}
\subfigure[moving patterns]{
\label{patterns} %% label for second subfigure
\includegraphics[width=2in]{example-line.png}}
\subfigure[POIs in region I]{
\label{POI} %% label for second subfigure
\includegraphics[width=2in]{example-POIs.png}}
\subfigure[Sentiment labels with their probability]{
\label{sentiment} %% label for second subfigure
\includegraphics[width=2in]{example-sentiment.png}}
\caption{The explanation provided for functional region identification.
Region I in Fig.\ref{real-map} is labeled as commercial region.
Fig.\ref{patterns} revealed the mobility patterns in the region,which weekends and evenings has more patterns than work time.
Fig.\ref{POI} shows that there is more shops than other POIs within this region.And from fig.\ref{sentiment} we find that people have a positive sentiment in traffic(label 18) and a negative sentiment in noise(label 25).}
\label{explanation-example} %% label for entire figure
\end{figure}

\subsection{challenge}
In order to solve the problem,we face two challenges.

The first one of it is to extract the urban feature from comment data.Urban feature is a set of attributes that could describe characters of the Corresponding region,e.g. traffic,noise,neighbors and so on.
Part of our content data comes from social media without detailed coordinates.They are full of sentiment tendencies but have difficulty to induced to a particular region.
The rest are comments of shops with the shop address.The feature extracted from it is more related to shop feature than urban feature.Due to the case,existing sentiment extraction model Sentires~\cite{Zhang2015Sentires} are infeasible in our models.%urban feature
In order to get the location information from these content data,we....

And the second challenge is that find the function of region is changing with time.The former research regarded time as a distinctive attribute of the region,put it as an input of DRoF model instead of describe its change~\cite{Yuan2012FunctionRegion}.%zheng 's time

%function = distribution of activitys and opinions

%previous research

@@

Our paper has an outstanding result in following several aspect:
\begin{itemize}
  \item To the best of our knowledge,we are the first to give explanation to urban functional region identification , which could improve the trustiness and satisfaction of user.
  \item We combined the sentiment and human mobility as explanation,find the urban feature within a region.
  %\item 3
\end{itemize}

@@

Two lines of work are related to this paper: urban computing and online sentiment analysis .

@@

Urban computing~\cite{Zheng2014UrbanConcepts} tackles the major issues that cities face by analyzing human mobility collected from different sensors.
Major sources of human mobility data are check-ins in POI~\cite{Gallegos16happier}, pick-up and drop-off behavior of taxicabs~\cite{Ge2011TaxiBusiness,Meng2017Traffic} in different locations and  trajectories.

%extract the different among these data
The simplest form of mobility data is check-ins data, which are collected from locating sharing services. Check-ins data usually includes a set of point revealing users' current location.
Statistical association analysis is commonly conducted on check-ins. For example, radius of gyration is measured in~\cite{Cheng2011Check-in}, which is extended by combining with lexicon into demographics~\cite{Gallegos16happier}.
A few recent work adopts model based approaches, e.g. context-aware tensor factorization that take account of contextual factors that influence consumers’ refueling decision~\cite{Zhang2015Fuel}.

The second form of mobility data is origin-destination pairs, i.e. a pick-up point and a drop-off point of a taxi trajectory.
Clustering methods including Newman modularity cluster algorithm~\cite{Newman2004ModularityFunction} are applied in functional region identification~\cite{Ratti2010Telecom}.
Recently, latent factor models are proposed to treat a region as document and infer functional-specific ~\cite{Yuan2012FunctionRegion}.%
Latent activity is imported in topic model in~\cite{Yuan2015FunctionRegion} to define the specific functions of different regions.

Alternatives for origin-destination pairs are trajectory data.
Applications on trajectory data include recommendation, e.g. to recommend more suitable place to drivers~\cite{Ge2011TaxiBusiness,Garg2018Route} and traffic planning, e.g. to find reachable region within a given temporal period~\cite{Wu2017Reachable}, %find a fast route
or to predict travel time~\cite{Wang2018Deep}.

%tasks
However, existing urban computing systems extensively rely on complex machine learning algorithms hence they act as blank-boxes for end users.
The lack of explanation weakens the persuasiveness and trustworthiness of the system for users.
Our work is to make up for this drawback by providing intuitive explanations of the results for users or system designers

@@

Recently, an emerging research interest is witnessed in exploring the geographical factors that affect online sentiment.
Empirical studies have been conducted on large-scale human mobility data, such as check-in ~\cite{Gallegos16happier}and trajectory~\cite{González2008Track},to find the geographical content analysis with sentiment.
Associations are found between online sentiments and geographical factors, e.g happy regions are more likely to connect with each other~\cite{Alshamsi15milan},a high check-in density region usually presents a more positive mode~\cite{Gallegos16happier}, the whole process and development of a organized movement could be tracked on the social media~\cite{Alvarez2015Movement} and so on.

%and emotion
%complete survey
However, most existing work of this line employ simple statistical analysis to uncover the associations.
Such a coarse-grained analysis is distorted by latent variables, such as activity of the region.
Our work is the first to incorporate activity to obtain a fine-grained analysis.

@@

\section{Experiments}
\subsection{Data Set}
The data set for our experiments including both mobility data and content data.
The mobility data including the pick-up and drop-off time and coordinates in November of the year 2016 provided by DiDi, the biggest taxi platform in China.It contributed to the movement pattern of human mobility.
And the online content is crawled from a website with many comments similar to Yelp called DazhongDianping and a social media named Weibo , which helps sentiment analysis of the regions.

@@

\begin{thebibliography}{25}
\bibitem{Zheng2014UrbanConcepts}Zheng Y, Capra L, Wolfson O, et al. Urban Computing:Concepts, Methodologies, and Applications[J]. Acm Transactions on Intelligent Systems \& Technology, 2014, 5(3):1-55.
    %综述城市计算的概念和框架
\bibitem{Zheng2011taxicabs}Zheng Y, Liu Y, Yuan J, et al. Urban computing with taxicabs[C]// International Conference on Ubiquitous Computing. ACM, 2011:89-98.
    %利用GPS轨迹检测出现有城市规划中存在的缺陷。结果包括：1）存在显著交通问题的区域对，2）连接结构以及它们之间的相关性。这些结果可以评估所实施的规划的有效性，例如一个城市新建的公路和地铁线路，并提醒城市规划者在构思未来规划时没有认识到的问题。
\bibitem{Meng2017Traffic}Meng, C.; Yi, X.; Su, L.; Gao, J.; Zheng, Y. City-wide Traffic Volume Inference with Loop Detector Data and Taxi Trajectories. Proceedings of the 25th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems,ACM,2017, 1:1-1:10
    %提出了一个框架来推断城市交通流量信息与环路探测器和出租车轨迹。

\bibitem{Vatsavai2011Remote}Vatsavai R R, Bright E, Varun C, et al. Machine learning approaches for high-resolution urban land cover classification:a comparative study[C]// International Conference and Exhibition on Computing for Geospatial Research \& Application, Com.geo 2011, Washington, Dc, Usa, May. DBLP, 2011:1-10.
    %利用遥感数据生成主题地图
\bibitem{Vatsavai2010Remote}Vatsavai R R, Cheriyadat A, Gleason S. Unsupervised Semantic Labeling Framework for Identification of Complex Facilities in High-Resolution Remote Sensing Images[C]// IEEE International Conference on Data Mining Workshops. IEEE Computer Society, 2010:273-280.
    %利用遥感数据生成主题地图

\bibitem{Ratti2010Telecom}Ratti C, Sobolevsky S, Calabrese F, et al. Redrawing the Map of Great Britain from a Network of Human Interactions[J]. Plos One, 2010, 5(12):e14248.
    %利用电信数据库来划分地图。
\bibitem{Yuan2010NextPassenger}Yuan J, Zheng Y, Zhang L, et al. Where to find my next passenger[C]// Proceedings of the 13th international conference on Ubiquitous computing. ACM, 2011:109-118.
\bibitem{Ge2011TaxiBusiness}Ge Y, Liu C, Xiong H, et al. A taxi business intelligence system[C]// ACM SIGKDD International Conference on Knowledge Discovery and Data Mining, San Diego, Ca, Usa, August. DBLP, 2011:735-738.
    %利用轨迹点来提升司机收入
\bibitem{Farmer2009Overview}Farmer, C. J. (2009). Data driven functional regions. In Proceedings of 10th International Conference on GeoComp
    %对之前的functional region做了一个总结。

@@

\bibitem{Goddard1970EarliestFunction}Goddard J B. Functional Regions within the City Centre: A Study by Factor Analysis of Taxi Flows in Central London[J]. Transactions of the Institute of British Geographers, 1970, 49(49):161-182.
    %最早提出用出租车轨迹来做功能区划分。但是早期数据都来自司机填写调查问卷，不够准确且数据较小，因此研究的东西比较初步，只能表明伦敦中心区包含许多具有强大内部联系的非常独立的功能区。
\bibitem{Karlsson2006FunctionalRegionSummary}Karlsson C, Olsson M. The identification of functional regions: theory, methods, and applications[J]. Annals of Regional Science, 2006, 40(1):1-18.
    %对现有（2006）的功能区识别方法做了总结，将方法归纳为三类：
    %（1）基于不同城市核心区之间通勤频率的比较的当地劳动力市场方法
    %（2）通勤区方法（Killian等。1993年，它建立在现有的城市相互依存的基础上，并衡量地区之间双向通勤联系的强度
    %(3)无障碍方法，它利用两种无障碍方式：雇主与工人的接触。获得工作机会。
\bibitem{Newman2004ModularityFunction}Newman M E J. Detecting community structure in networks[J]. European Physical Journal B, 2004, 38(2):321-330.
    %模块化方法的鼻祖
\bibitem{Ball1980Definition}R.M. Ball. The use and definition of Travel-to-Work Areas in Great Britain: Some problems[J]. Regional Studies, 1980, 14(2):125-139.
    %早期的Urban function定义

@@

    %引入latent activity，对他自己2012的论文做了一个拓展，提高精确度
    %对之前functional region工作的一个总结，没有再加入新的提高
\bibitem{Zhang2015Fuel}Zhang F, Yuan N J, Wilkie D, et al. Sensing the Pulse of Urban Refueling Behavior:A Perspective from Taxi Mobility[J]. Acm Transactions on Intelligent Systems \& Technology, 2015, 6(3):1-23.
    %提出了一个智能系统，用于利用出租车轨迹、POI、道路网络和在线用户的报告来发现城市加油行为。
\bibitem{Shang2014Pollution}Shang J, Zheng Y, Tong W, et al. Inferring gas consumption and pollution emission of vehicles throughout a city[J]. 2014:1027-1036.
    %本文利用车辆轨迹（例如出租车）的GPS轨迹，即时推断出在城市时速路段上行驶的车辆的气体消耗量和污染排放量。
\bibitem{Wu2017Reachable}Wu G, Ding Y, Li Y, et al. Mining Spatio-Temporal Reachable Regions over Massive Trajectory Data[C]// IEEE, International Conference on Data Engineering. IEEE, 2017:1283-1294.
    %寻找时空可达区域

@@

\bibitem{Wang2018Deep}D Wang,J Zhang,W Cao,J Li,Y Zheng.When Will You Arrive? Estimating Travel Time Based on Deep Neural Networks.In International AAAI Conference on Web and Social Media, 2011.
    %用深度神经网络来预测旅行时间

@@

\bibitem{Alvarez2015Movement}R. Alvarez, D. Garcia, Y. Moreno, and F. Schweitzer. Sentiment cascades in the 15m movement. EPJ Data Science, 4(1):1–13, 2015
    %从社交网站上挖掘15M这个运动的组织、形成与爆发

@@

\bibitem{Cheng2011Check-in}Z. Cheng, J. Caverlee, K. Lee, and D. Sui. Exploring millions of footprints in location sharing services. In International AAAI Conference on Web and Social Media, 2011.
    %check-in数据来自整个美国.         用户有周期性的行为模式（weekly），受地理、经济、个人社会地位（粉丝越多地位越高）约束，需要content来更好地理解.引入回转半径来帮助sentiment（实际文本分析还是靠字典）
\bibitem{González2008Track}González M C, Hidalgo C A. Understanding individual human mobility patterns[J]. Nature, 2008, 453(7196):779-782.
    %追踪100000名手机用户6个月，人体轨迹表现出高度的时间和空间规律。说是human mobility, 但是数据集是长期轨迹包含很多点

@@

\bibitem{Preece2018ExplainAI}Preece A. Asking 'Why' inAI: Explainability of intelligent systems - perspectivesand challenges. Intell Sys Acc Fin Mgmt. 2018;25:63–72.
    %explain AI
\bibitem{Korpan2017navigation}Korpan, R., Epstein, S.L., Aroor, A., Dekel, G.: WHY: Natural explanations from a robot navigator. In: AAAI 2017 Fall Symposium on Natural Communication for Human-Robot Collaboration.
\bibitem{Jose2018cognitive}Jose M. Alonso, Corrado Mencar. Building Cognitive Cities with Explainable Artificial Intelligent Systems,2018
